Final presentation

Element 1) Density plots of each variable (Rose)
Describing the data, univariate requirement
Will include a table of min, max, SD

```{r, echo=FALSE, results='hide'}
#Rose's code for showing density plots and categorical lolliplots

#Step 1, bring in the data, create data frame
data <- read.csv("eardata.csv")
data <- as.data.frame(data)

#Step 2, create density plots for indicies with median line
library(ggplot2)
Ginibase=ggplot(data,aes(x = Gini))+stat_density(geom = "line")+theme_classic()+labs(x='Inequality', y= NULL)+geom_vline(aes(xintercept=median(Gini)),
            color="gray", linetype="dashed", size=.5)

Justicebase=ggplot(data,aes(x = JusticeIndex))+stat_density(geom = "line")+theme_classic()+labs(x='Justice', y= NULL)+geom_vline(aes(xintercept=median(JusticeIndex)),
            color="gray", linetype="dashed", size=.5)

PHIbase=ggplot(data,aes(x = PHI))+stat_density(geom = "line")+theme_classic()+labs(x='Pregnancy Health', y= NULL)+geom_vline(aes(xintercept=median(PHI)),
            color="gray", linetype="dashed", size=.5)

Dependencybase=ggplot(data,aes(x=DependencyScore))+stat_density(geom = "line")+theme_classic()+labs(x='Federal Dependency', y=NULL)+geom_vline(aes(xintercept=median(DependencyScore)),
            color="gray", linetype="dashed", size=.5)

#Combining into one plot
library(ggpubr)

DensityAll <-ggarrange(Ginibase,Justicebase,PHIbase,Dependencybase, ncol = 1,nrow = 4)

DensityAll2 = annotate_figure(DensityAll,
                            top = text_grob("Distribution of Indicies: Positive Skew for Justice, Pregnancy Health, and Federal Dependency",
                                            face = "bold", size = 11),
                            bottom = text_grob("Sources: ACS, 2010; National Center for Access to Justice, 2016; CDC, 2017; Guttmacher Institute, 2014; FEDERAL DEPENDENCY SOURCE", 
                                               hjust = 1, x = 1,
                                               face = "italic", 
                                               size = 8),
                            left = 'Density',
                            right = NULL)

DensityAll2

#Step 4, create lolliplots comparing Inequality and Pregnancy Health (most intersting comparisson)

#Create data frame - Inequality
summary(data$Gini)
data$GiniGroup =cut(data$Gini,
                          breaks = c(0.4,0.452,0.4673,0.4789,0.53),
                          #labels = c("1st Quartile","2nd Quartile","3rd Quartile", "4th Quartile"))
                          labels = c("Low"," ","  ","High"))

#marginal data frame - Inequality 
(GiniRegion=table(data$GiniGroup,data$Region))

GiniRegion_mgcol=prop.table(GiniRegion,
                              margin = 2)

GiniRegion_df<-as.data.frame(GiniRegion)
names(GiniRegion_df)
names(GiniRegion_df)<-c("GiniGroup","Region","Count")

GiniRegion_df$pctCol=as.data.frame(GiniRegion_mgcol)[,3]
head(GiniRegion_df)

#Create data frame - Pregnancy Health
summary(data$PHI)
data$PHIGroup =cut(data$PHI,
                          breaks = c(0.17,0.2062,0.2273,0.2541,0.33),
                          #labels = c("1st Quartile","2nd Quartile","3rd Quartile", "4th Quartile"))
                          labels = c("Low"," ","  ", "High"))

#marginal data frame - Pregnancy Health
(PHIRegion=table(data$PHIGroup,data$Region))

PHIRegion_mgcol=prop.table(PHIRegion,
                              margin = 2)

PHIRegion_df<-as.data.frame(PHIRegion)
names(PHIRegion_df)
names(PHIRegion_df)<-c("PHIGroup","Region","Count")

PHIRegion_df$pctCol=as.data.frame(PHIRegion_mgcol)[,3]
head(PHIRegion_df)

#Create lolliplot - Inequality
lolliplotGini = 
  ggplot(GiniRegion_df, 
                 aes(x = GiniGroup,
                     y = pctCol) ) + 
  geom_segment(aes(y = 0,
                   x = GiniGroup,  
                   yend = pctCol, #ends at the pct value
                   xend = GiniGroup)) + facet_grid( ~ Region) +
  geom_point()+theme_bw()+
  labs(y= "Inequality", 
       x=NULL)+ylim(0, .9)

#Create lolloplot - Pregnancy Health
lolliplotPHI = 
  ggplot(PHIRegion_df, 
                 aes(x = PHIGroup,
                     y = pctCol) ) + 
  geom_segment(aes(y = 0,
                   x = PHIGroup,  
                   yend = pctCol, #ends at the pct value
                   xend = PHIGroup)) + facet_grid( ~ Region) +
  geom_point()+theme_bw()+
  labs(y= "Pregnancy Health", 
       x=NULL)+ylim(0, .9)

#Group and label two plots
LolliAll_1 <-ggarrange(lolliplotGini,lolliplotPHI, ncol = 1,nrow = 2)

LolliAll_2= annotate_figure (LolliAll_1,
                            top = text_grob("Pregnancy Health Best in Northeast, High Inequality and Low Pregnancy Health in South",
                                            face = "bold", size = 11),
                            bottom = text_grob("Sources: ACS, 2010; CDC, 2017; Guttmacher Institute, 2014", 
                                               hjust = 1, x = 1,
                                               face = "italic", 
                                               size = 8))

LolliAll_2
```

Element 2) Correlation between indices (Ellen)
Shows relationship between indices, bivariate continuous continuous requirement

Health by Justice
```{r, echo=FALSE, results='hide'}

a=ggplot(data, aes(x=JusticeIndex, y=PHI)) + geom_point()+
  geom_smooth(method=lm) + labs(x="Justice", y="Pregnancy Health") + theme_classic()

b=ggplot(data, aes(x=Gini, y=PHI)) + geom_point()+
  geom_smooth(method=lm) + labs(x="Inequality", y="Pregnancy Health") + theme_classic()

c=ggplot(data, aes(x=JusticeIndex, y=Gini)) + geom_point()+
  geom_smooth(method=lm) + labs(x="Justice", y="Inequality") + theme_classic()

library(ggpubr)

multireg = ggarrange(a,b,c,ncol = 3,nrow = 1)

title <- expression(atop(bold("Trends by Indices"), scriptstyle("Note: pregnancy health increases with justice and decreases with higher inequality")))
multireg2 = annotate_figure(multireg,
                            top = text_grob(title,
                                            face = "bold", size = 16),
                            bottom = text_grob("Sources: ACS, 2010; National Center for Access to Justice, 2016; CDC, 2017; Guttmacher Institute, 2014",
                                               hjust = 1, x = 1,
                                               face = "italic",
                                               size = 10),
                            left = 'Density',
                            right = NULL)


multireg2
```


Element 3) Variation of indices between regions (Rose) - take out dependency
Shows relationships between categories, bivariate cat-cat requirement 

```{r, echo=FALSE, results='hide'}

```


Element 4) Maps that show “better” states compared to federal dependency (Alex) - add in dependency
Creates super index for “good social outcomes” 
Compares this map to map of above average/below average for federal dependency and the super index

```{r, echo=FALSE, results='hide'}

```


Element 5) Conclusions

```{r, echo=FALSE, results='hide'}

```

